---
title: "Sagebrush_Mort"
author: "Lindsay Chaney"
date: "July 23, 2015"
output: html_document
---

This is the results of the sagebrush mortality paper.

```{r run, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
source('~/GitHub/Sagebrush_Mort/Analysis/04_SM_do.R')
```

##Survival for all 3 gardens
2 by 2 kaplain meyer plot for all 3 gardens

```{r km22plot, echo = FALSE, warning = FALSE, error = FALSE}
	km22plot
```	

summary of moratality at all 3 gardens
```{r surv3summary, echo = FALSE, warning = FALSE, error = FALSE}
surv3summary
```	

sample sizes tables for all 3 gardens, I'll just display the first couple rows to save space 
```{r surv3dsample, echo = TRUE, warning = FALSE, error = FALSE}
	head(surv3dsample)
```

##Contemporary Climate data
print death and climate plot for all 3 gardens
```{r deathclim, echo = FALSE, warning = FALSE, error = FALSE}
	plot(deathclim)
```


print out minimum monthly minimum temperatures by garden
```{r mintempsmonth, echo = FALSE, warning = FALSE, error = FALSE}
  mintempsmonth
```

##Ephraim survival data

print survival regression (Table 2)

```{r summary_ephsurvlogn, echo = FALSE, warning = FALSE, error = FALSE}
	summary_ephsurvlogn
```

print kaplien meyer plot with survival regression curves (Figure 1)
```{r ephsurvplot_lognorm, echo = FALSE, warning = FALSE, error = FALSE}
	ephsurvplot_lognorm
```	

Print log rank test for survival curves
```{r svdatlrtest, echo = FALSE, warning = FALSE, error = FALSE}
	svdatlrtest
```	
print posthoc pairwise comparison table of chisquare log-rank test and pvalues
```{r lrchisqtable, echo = FALSE, warning = FALSE, error = FALSE}
	lrchisqtable
	pval_lrchisqtagible
```
Note that the new bonferoni corrected p-value for significance is `r newbfp`
		
Median survival is as follows
```{r medsurv, echo = FALSE, warning = FALSE, error = FALSE}
	medsurv
```

Probability of survival at different months -- column survival gives you those times 
```{r probsurv, echo = FALSE, warning = FALSE, error = FALSE}
	probsurv1
	probsurv2	
```

##Ephraim climate survival data
Here is the generalized linear model with r squared value and model coefficients

```{r climsurv, echo = FALSE, warning = FALSE, error = FALSE}
	climsurv
	climsurvrsq
	coefclimsurv
```

And for now that is my results.