---
title: "Adaptive genetic response to climate affects survival 
in Artemesia tridentata (big sagebrush)"
author: "Lindsay Chaney, Bryce Richardson"
date: "December x, 2015"
output:
  html_document:
    toc: true
    theme: spacelab
---

# Abstract:

> A genecological approach was used to explore genetic variation in survival in in Artemisia tridentata (big sagebrush). Artemisia tridentata is a fundamental shrub species in western North America, large declines of this species and its affect on associated wildlife has resulted in increased conservation and restoration efforts. Common garden experiments were established at three sites with seedlings from 55 sources populations . Populations included each of the three predominant subspecies, A. t. tridentata, A. t. wyomingnesis, and A. t. vaseyana, and ploidy types. Survival was monitored for five-years to assess differences in survival between gardens and populations. 
We found evidence of adaptive geographic variation for survival in A. tridentata. Survival within gardens differed by population and is predicted by climate of the seed source. Plants from more continental climates (greater summer-winter temperature differences) had the highest levels of survival while populations from warmer and drier sites had the highest levels of mortality. Survival differed between gardens and is driven by winter minimum temperatures in association with atmospheric decoupling. Understanding how genetic variation is arrayed across the landscape through association with climate can greatly enhance the success of restoration and conservation.

*Here I will present figures and results from R analysis presented in order adressed in the paper.*

```{r run, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, fig.keep='none'}
source('Analysis/04_SM_do.R')
```

## Supplementary Table 1
Population information from seed source location.

```{r surv3dsample, echo = FALSE, warning = FALSE, error = FALSE}
	surv3dsample #sample sizes table for all 3 gardens
```

## Table 1
Geographic and climatic attributes of the three common gardens.

*find in text*

## Supplementary Figure 1
Experimental design includes three common garden locations (stars) and 55 source populations (pentagons). Populations are seed source locations of three big sagebrush subspecies and two ploidy levels, or types (indicated by colored pentagons). Type: T4x = tetraploid tridentata; T2x = diploid tridentata; W4x = tetraploid wyomingensia; V2x = diploid vaseyana; V4x = tetraploid vaseyana.

*Generated in QGis*

## Table 2
Generalized linear model of survival proportion of each population.

```{r glm3, echo = FALSE, warning = FALSE, error = FALSE}
aovfit3
```	

## Supplementary Figure 2
Kaplien-Meir survivorship curves for big sagebrush by (a) common garden and survivor ship by type (subspecies:ploidy) for the (b) Ephraim, (c) Majors Flat and (d) Orchards garden. 

```{r km22plot, echo = FALSE, warning = FALSE, error = FALSE}
	km22plot
```	

And a summary of moratality at all 3 gardens

```{r surv3summary, echo = FALSE, warning = FALSE, error = FALSE}
surv3summary
```	

## Supplementary Figure 3
Interaction plot of genetics and environment for each population. Each line indicates survival proportion for a given population in each respective common garden.

```{r glm3int, echo = FALSE, warning = FALSE, error = FALSE}
int_plot
```	

## Figure 1
Kaplien-Meir survivorship curves by type (subspecies:ploidy) in big sagebrush. Model estimates of the log-normal survivorship curve from the survivorship regression is overlaid to assess fit of model. Survivorship was significantly different by type (subspecies: ploidy).
print kaplien meyer plot with survival regression curves (Figure 1)

```{r ephsurvplot_lognorm, echo = FALSE, warning = FALSE, error = FALSE}
	ephsurvplot_lognorm
```	

Log rank test for survival curves in Eprhaim
```{r svdatlrtest, echo = FALSE, warning = FALSE, error = FALSE}
	svdatlrtest
```	

Posthoc pairwise comparison table of chisquare log-rank test, pvalues, and
bonferroni corrected p values.
```{r lrchisqtable, echo = FALSE, warning = FALSE, error = FALSE}
	lrchisqtable
	pval_lrchisqtagible
	pval_lrchisqtagiblebonf
```

## Supplementary Table 2
Analysis of big sagebrush by type (subspecies:ploidy) using  regression for a parametric survival model (accelerated failure time).
This model assumes that survival time changes by a constant factor when comparing different levels of covariates. Type T4x is the baseline (intercept) value. The coefficient value is the factor by which the survival time is multiplied for that covariate compared to the baseline. The scale indicates how the rate of survival changes over time. The z-values and p-values are used to test for statistical significance of any difference between groups. Type: T4x = tetraploid tridentata; T2x = diploid tridentata; W4x = tetraploid wyomingensia; V2x = diploid vaseyana; V4x = tetraploid vaseyana

```{r summary_ephsurvlogn, echo = FALSE, warning = FALSE, error = FALSE}
	summary_ephsurvlogn
```

## Supplementary Table 3
Probability of and median survival for each type of big sagebrush.
Probability of survival shown for 12, 24, 36, 48 and 59 months and median survival shows at which month there is 50% chance of survival. 

```{r med_probsurv, echo = FALSE, warning = FALSE, error = FALSE}
	medsurv
	probsurv
```

##Figure 2
Proportion survival in Ephraim garden for each source population. Diagram indicates proportion of survival for each population, dark color indicates mortality while the light color indicates survival. Color of each population is determined by type (subspecies:ploidy).
Type: T4x = tetraploid tridentata; T2x = diploid tridentata; W4x = tetraploid wyomingensia; V2x = diploid vaseyana; V4x = tetraploid vaseyana

*Generated in QGis*

## Table 3
Generalized linear model for proportion survival of big sagebrush in the Ephraim garden.
Type, the subspecies ploidy combination, and provenance (source population) climate variables GSPMTCM and SDAY explain most variation in the model (R2 = 0.757). GSPMTCM: interaction of growing season precipitation (Apr-Sep) and mean temperature in coldest moth; SDAY: Julian date of the last freezing day of the spring

```{r climsurv, echo = FALSE, warning = FALSE, error = FALSE}
	climsurv
	climsurvrsq
	coefclimsurv
```

## Figure 3
Bioclimatic model of survivorship in big sagebrush. Log-link transformed coefficients of slopes and intercepts of the provenance climate model was used to project probability of survival into the niche boundaries of wyomingnesis big sagebrush. Climate predictors included in the model are SDAY and GSPMTCM. Areas that are cooler and wetter have higher probability of survival (blue) while areas that are warmer and drier have lower probability of survival (red).
SDAY: Julian date of the last freezing day of the spring; GSPMTCM: interaction of growing season precipitation (Apr-Sep) and mean temperature in coldest month.

*Generated in QGis*

## Supplementary Figure 4
Top panel shows minimum daily temperatures (light lines) with 30 day moving averages (bold lines) for the three garden locations during the experimental time period. Bottom panel shows number of deaths for each garden at each of the census times. Ephraim (red), Majors Flat (purple) and Orchards (turquoise) garden.

```{r deathclim, echo = FALSE, warning = FALSE, error = FALSE}
	plot(deathclim)
```

## Supplementary Table 4
Probability of  survival, median survival, and mortality numbers for each population of big sagebrush in the Ephraim common garden.

```{r popsurv, echo = FALSE, warning = FALSE, error = FALSE}
	poplrtest
	popmedsurv
	popprobsurv
```
